Cooling Requirements for the Vertical Shear Instability in Protoplanetary Disks

### 2015-05-06 appendix.tex
another round of edits to 7 with a few italics comments remaining.  shortened version of appendix E moved to main text.

\section{Fiducial model for a protoplanetary disk}\label{mmsn}
For results application in \S\ref{application} we use the disk model
described in \cite{chiang10}. This disk model orbits a Solar-mass star and 
has the surface density distribution
\begin{align}\label{mmsn_sigma}
  \Sigma = 2200
  \hat{\Sigma}\left(\frac{r}{\mathrm{AU}}\right)^{-3/2}\mathrm{g}\,\mathrm{cm}^{-2},  
\end{align}
and the temperature profile
\begin{align}\label{mmsn_temp}
  T = 120\hat{T}\left(\frac{r}{\mathrm{AU}}\right)^{-3/7} \mathrm{K},
\end{align}
which implies $q=-3/7$. In the above expressions, $\hat{\Sigma}$ and
$\hat{T}$ are dimensionless coefficients used to scale the model
relative to the MMSN. By assuming a
vertically isothermal disk, we deduce the disk aspect-ratio 
\begin{align}\label{mmsn_epsilon}
  h =
  3.36\times10^{-2}\left(\frac{\hat{T}}{\mu}\right)^{1/2}\left(\frac{r}{\mathrm{AU}}\right)^{2/7}, 
\end{align}
and the mid-plane density distribution 
\begin{align}
%  \rho_0 = 2.7\times10^{-9}
%  \hat{\upsilon}\left(\frac{r}{\mathrm{AU}}\right)^{-39/14}\mathrm{g}\,\mathrm{cm}^{-3},  
\rho_0 = 1.7\times10^{-9}
  \hat{\Sigma}\left(\frac{\hat{T}}{\mu}\right)^{-1/2}\left(\frac{r}{\mathrm{AU}}\right)^{-39/14}\mathrm{g}\,\mathrm{cm}^{-3},
\end{align}
which implies $p=-39/14$. 
%0.033576258
In addition, we use the opacity model
 \begin{align}
   \kappa_d &= 2 \hat{\kappa}_d \left(\frac{T}{100\mathrm{K}}\right)^2
   \mathrm{cm}^2\,\mathrm{g}^{-1}
    =
   2.88\hat{\kappa}_d\hat{T}^2\left(\frac{r}{\mathrm{AU}}\right)^{-6/7}\mathrm{cm}^2\,\mathrm{g}^{-1},   
 \end{align}
\citep{bell94} where the second equality follows from the model
temperature profile above, and $\hat{\kappa}_d$ has similar meaning as
$\hat{\Sigma}$ and $\hat{T}$. In \S\ref{application} we fix
$\hat{\Sigma} = \hat{T}=1$, $\mu=2.33$ and use $\gamma=1.4$.

>>>>

%\section{Fiducial model for a protoplanetary disk}\label{mmsn}
%For results application in \S\ref{application} we use the disk model
%described in \cite{chiang10}. This disk model orbits a Solar-mass star and 
%has the surface density distribution
%\begin{align}\label{mmsn_sigma}
%  \Sigma = 2200
%  \hat{\Sigma}\left(\frac{r}{\mathrm{AU}}\right)^{-3/2}\mathrm{g}\,\mathrm{cm}^{-2},  
%\end{align}
%and the temperature profile
%\begin{align}\label{mmsn_temp}
%  T = 120\hat{T}\left(\frac{r}{\mathrm{AU}}\right)^{-3/7} \mathrm{K},
%\end{align}
%which implies $q=-3/7$. In the above expressions, $\hat{\Sigma}$ and
%$\hat{T}$ are dimensionless coefficients used to scale the model
%relative to the MMSN. By assuming a
%vertically isothermal disk, we deduce the disk aspect-ratio 
%\begin{align}\label{mmsn_epsilon}
%  h =
%  3.36\times10^{-2}\left(\frac{\hat{T}}{\mu}\right)^{1/2}\left(\frac{r}{\mathrm{AU}}\right)^{2/7}, 
%\end{align}
%and the mid-plane density distribution 
%\begin{align}
%%  \rho_0 = 2.7\times10^{-9}
%%  \hat{\upsilon}\left(\frac{r}{\mathrm{AU}}\right)^{-39/14}\mathrm{g}\,\mathrm{cm}^{-3},  
%\rho_0 = 1.7\times10^{-9}
%  \hat{\Sigma}\left(\frac{\hat{T}}{\mu}\right)^{-1/2}\left(\frac{r}{\mathrm{AU}}\right)^{-39/14}\mathrm{g}\,\mathrm{cm}^{-3},
%\end{align}
%which implies $p=-39/14$. 
%%0.033576258
%In addition, we use the opacity model
% \begin{align}
%   \kappa_d &= 2 \hat{\kappa}_d \left(\frac{T}{100\mathrm{K}}\right)^2
%   \mathrm{cm}^2\,\mathrm{g}^{-1}
%    =
%   2.88\hat{\kappa}_d\hat{T}^2\left(\frac{r}{\mathrm{AU}}\right)^{-6/7}\mathrm{cm}^2\,\mathrm{g}^{-1},   
% \end{align}
%\citep{bell94} where the second equality follows from the model
%temperature profile above, and $\hat{\kappa}_d$ has similar meaning as
%$\hat{\Sigma}$ and $\hat{T}$. In \S\ref{application} we fix
%$\hat{\Sigma} = \hat{T}=1$, $\mu=2.33$ and use $\gamma=1.4$.
